Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-27 analysis/paper/paper.Rnw
fixed missing chunk problem in Rnw file

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
%\usepackage{etoolbox} % for messing with page style & title pages
\usepackage{lscape}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}%

@@

<<heat9-2, fig.height = 7, fig.width = 7, out.width = "\\textwidth">>=
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
p
@

@@

@@

@@

@@

@@

@@

@@

>>>>

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
%\usepackage{etoolbox} % for messing with page style & title pages
%\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}%

@@

<<heat9-2>>=
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnhtml <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.html"))
fnpdf <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.pdf"))
htmlwidgets::saveWidget(widget = p,
                        file = fnhtml
                        )
webshot::webshot(url = fnhtml,
                 file = fnpdf,
                 cliprect = "viewport"
                 )
@

\newpage
\begin{landscape}

<<hm_plot-2>>=
knitr::include_graphics(path = paste0("../figures/Chr", hot_chr, "hm.pdf"))
@

\end{landscape}

@@

\newpage
\begin{landscape}

<<hm_plot-5, ref.label = "hm_plot-2">>=

@

\end{landscape}

@@

<<make_nonlocal_annot-7, ref.label = "make_nonlocal_annot-2">>=
@

@@

\newpage
\begin{landscape}

<<hm_plot-7, ref.label = "hm_plot-2">>=

@

\end{landscape}

@@

<<make_nonlocal_annot-11, ref.label = "make_nonlocal_annot-2">>=
@

@@

\newpage
\begin{landscape}

<<hm_plot-11, ref.label = "hm_plot-2">>=

@

\end{landscape}

@@

<<make_nonlocal_annot-13, ref.label = "make_nonlocal_annot-2">>=
@

@@

\newpage
\begin{landscape}

<<hm_plot-13, ref.label = "hm_plot-2">>=

@

\end{landscape}
